Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-18 final_metrics_analysis.Rmd

```{r py setup, include=FALSE}
library(reticulate)
use_condaenv("anaconda3")
```

@@

>>>>

```{r py setup, include=FALSE}
library(reticulate)

# for Dianne
use_condaenv("base")

# for Amrita
# use_condaenv("anaconda3")
#use_condaenv("anaconda3")
```

@@

```{python make degree numeric}
#av_defendant = (df_viz.groupby(['race'],as_index=False).age.mean()
#display(df_viz)
#list_vars = list(df_viz)
#list_vars
#df_numeric_charges = df_viz['c_charge_degree'].replace(['M', 'F'], [0, 1], inplace=True)
#plt.bar('c_charge_degree', 1, data = df_viz)
```
